\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{banking}
\moderncvcolor{black}

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust the page margins
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{3.5cm}

% Personal data
\name{Rudi}{Aj}
\phone[mobile]{+385~97~792~9943}
\email{aj.rudi@gmail.com}
\social[linkedin]{rudi-aj}
\homepage{rudiaj.dev}
\address{Rijeka, Croatia}{}{}

\begin{document}

\makecvtitle

\vspace{-20pt}
\begin{center}
\textbf{Senior Frontend Developer · 10 years of experience specializing in Next.js and React}
\end{center}

\section{Experience}

\cventry{Feb 2025 -- Present}{Co-founder}{Gled}{Remote}{}{%
\textit{Real estate B2B SaaS platform for property agents (Side project)}
\begin{itemize}
\item Built and launched a self-funded, profitable-from-day-one real estate B2B SaaS product that helps agents save time and discover new property listings on the market.
\item Achieved 100\% customer retention and organic paid growth through word-of-mouth recommendations from satisfied real estate agents.
\item Developed an automated property search tool that notifies agents immediately when new listings appear on major Croatian real estate platforms, enabling them to be the first to contact sellers.
\item Engineered a platform that distinguishes between private sellers and agency listings, with customizable filters for location, property type, and price range.
\end{itemize}}

\cventry{Jul 2025 -- Nov 2025}{Frontend Developer Contractor}{Elixirr}{Remote}{5 mos}{%
\textit{Digital consulting firm specializing in transformation and growth}
\begin{itemize}
\item Developed a custom registration flow and live race tracking website for the Nedbank Gravel Burn cycling event using Next.js, Payload CMS, GraphQL.
\item Built the live race platform from the ground up within a tight deadline, integrating real-time data feeds from Race Base Pro to deliver dynamic rider tracking, stage progress updates, and leaderboard changes.
\item Created a premium digital experience, bringing the seven-day gravel race through South Africa's Karoo to a global audience.
\end{itemize}}

\cventry{Apr 2024 -- Jan 2025}{Frontend Engineer}{PlayAI}{Remote}{10 mos}{%
\textit{AI voice platform for TTS models backed by Y Combinator, acquired by Meta}
\begin{itemize}
\item Implemented SEO strategies achieving top-3 Google rankings for keywords like ``AI voice generator'' and ``text to speech'', leading to 300\% increase in organic traffic (50K to 300K monthly visitors)
\item Enhanced site performance by 56\% and upgraded project architecture from Next.js pages to app router
\item Refactored project from static Next.js to customized Payload CMS architecture
\end{itemize}}

\cventry{May 2023 -- Apr 2024}{Frontend Engineer}{BRIX Holdings}{Remote}{1 yr}{%
\textit{Multi-brand franchising company specializing in food service chains}
\begin{itemize}
\item Led implementation and rewrite of three franchising landing pages from WordPress to Next.js + Prismic
\end{itemize}}

\cventry{Jan 2022 -- May 2023}{Frontend Engineer}{Dickey's Barbecue Pit}{Remote}{1 yr 5 mos}{%
\textit{World's largest and fastest growing barbecue franchise}
\begin{itemize}
\item Contributed to multiple franchising projects owned by the company.
\item Worked closely with designers during the planning phase of the OLO dashboard complete rewrite from the standalone React to a Next.js app. Initiated the frontend bootstrapping, taking the lead in selecting technologies and implementing best practices. Played a key role in the project rewrite, which successfully brought down hosting costs by 80\%.
\end{itemize}}

\cventry{Jul 2020 -- Nov 2021}{Frontend Engineer}{Accountable}{Remote}{1 yr 5 mos}{%
\textit{Series A FinTech startup, backed by Venture Capital, acquired by Visma for €110M}
\begin{itemize}
\item Enhanced application for dual-market functionality in Belgium and Germany with multilingual support for improved user engagement.
\item Integrated a bank account connection feature, automating payment reconciliation and providing real-time insights on tax obligations, enabling users to make informed financial decisions.
\end{itemize}}

\cventry{Jan 2020 -- Jun 2020}{Frontend Engineer}{TAIA}{Remote}{6 mos}{%
\textit{Modern AI-assisted translation platform}
\begin{itemize}
\item Played a pivotal role in refactoring and advancing TAIA Translations Platform from MVP to version 1 within a dynamic six-month period.
\end{itemize}}

\cventry{Nov 2017 -- Dec 2019}{Fullstack Engineer}{Signature Networks}{Rijeka · On-site}{2 yr 3 mos}{%
\textit{Digital agency}
\begin{itemize}
\item Worked closely with AutoScout24 in-house team, transforming their monolith-based structure to a modern React Web App.
\item Guided and mentored junior developers through coding best practices and project workflows.
\item Contributed as a core developer on in-house product - accounting app built using MERN stack.
\end{itemize}}

\cventry{Mar 2017 -- Sep 2017}{Frontend Engineer}{Digital Cube}{Belgrade · On-site}{7 mos}{%
\textit{Digital agency}
\begin{itemize}
\item Worked as a contributor on a fitness tracking app powered by AngularJS.
\end{itemize}}

\cventry{Jun 2016 -- Mar 2017}{Frontend Engineer}{Upwork/Freelance}{Belgrade · On-site}{9 mos}{%
\begin{itemize}
\item Worked on a few smaller projects developing my AngularJS and Wordpress skills.
\end{itemize}}

\cventry{Nov 2015 -- May 2016}{Frontend Engineer Intern}{OriginTrail}{Belgrade · On-site}{7 mos}{%
\textit{Verifiable Web for Decentralised \#AI}
\begin{itemize}
\item Started Frontend Engineer internship.
\end{itemize}}

\section{Education}

\cventry{2014 -- 2017}{B.S.c. Web Development}{SAE Institute}{}{}{}
\cventry{2008 -- 2012}{Web Designer}{Natural Science and Graphic School Rijeka}{}{}{}

\section{Technical Skills}

\cvitem{Strong}{TypeScript, JavaScript, HTML, CSS/SCSS, Next.js, React, Redux, Node.js, Express, Tailwind CSS, MUI, Bootstrap, Framer Motion, Styled Components, MongoDB, PostgreSQL, Payload, Prismic, Strapi, Supabase, Drizzle ORM, Webpack, Jest, Git, REST, GraphQL}

\cvitem{Familiar}{PHP, WordPress, jQuery, Figma, Adobe Illustrator, Adobe Photoshop}

\section{Languages}

\cvitem{}{English (Fluent) · Croatian (Native)}

\section{Interests}

\cvitem{}{Music · Guitar · Weightlifting · Jiu-Jitsu · Logo Design · Seinfeld}

\end{document}
